The \dealii Library, Version 9.7

### 2025-08-20 9.7/paper.tex
Fix a missing author in a list.

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Maximilian Bergbauer,
    Bruno Blais,
    Marc Fehling,
    Rene Gassm\"{o}ller,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Bruno Turcksin,
    David Wells,
    Michał Wichrowski,
  },
  pdftitle={The deal.II Library, Version 9.7, 2025},
}

>>>>

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Maximilian Bergbauer,
    Bruno Blais,
    Marc Fehling,
    Rene Gassm\"{o}ller,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Bruno Turcksin,
    Siarhei Uzunbajakau,
    David Wells,
    Michał Wichrowski
  },
  pdftitle={The deal.II Library, Version 9.7, 2025},
}
